---
title: "Data import"
author: "Boya Guo"
date: "9/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

`````

## Import FAS csv files 

Import my first csv using relative path.

```{r}
litters_data = read_csv(file="./data/FAS_litters.csv")
litters_data=janitor::clean_names(litters_data)
litters_data

pups_data = read_csv(file = "./data/FAS_pups.csv")
pups_data=janitor::clean_names(litters_data)
pups_data
`````

## Look at data 

Look at litters data 

```{r}
litters_data 
head(litters_data)
tail(litters_data)

skimr:: skim(litters_data)
`````

Skip some rows; omit variable names

```{r}
litters_data = read_csv(file = "./data/FAS_litters.csv",
  skip = 10, col_names = FALSE)
litters_data
`````

Repeat the data import process for the file FAS_pups 

```{r}
pups_data = read_csv("./data/FAS_pups.csv", col_types = "ciiiii")
pups_data= janitor::clean_names(pups_data)
skimr::skim(pups_data)
pups_data
`````

What happens if your specifications for column parsing aren’t reasonable (e.g. character instead of double, or vice versa)?

```{r}
pups_data = read_csv("./data/FAS_pups.csv", col_types = "diiiii")
pups_data= janitor::clean_names(pups_data)
skimr::skim(pups_data)
pups_data
`````
The first column will become all missing data.

## Other formats 

Read in mlb data

```{r}
library(readxl)
mlb11_data = read_excel("data/mlb11.xlsx", n_max = 20)
head(mlb11_data, 5)

mlb_subset=read_excel("data/mlb11.xlsx",range="A1:E17")
mlb_subset
`````

Read in pulse data

```{r}
library(haven)
pulse_data = read_sas("./data/public_pulse_data.sas7bdat")
head(pulse_data, 5)
pulse_data
`````

## Compare with base R

```{r}
pups_base = read.csv("./data/FAS_pups.csv")
pups_readr = read_csv("./data/FAS_pups.csv")

View(pups_base)
View(pups_readr)

pups_base
pups_readr

pups_base$S
pups_readr$S
`````
