---
title: "data_wrangling_ii_strings_and_factors"
author: "Boya Guo"
date: "10/16/2018"
output: html_document
---

String: just the text, character varaible, no underlying structures 

Factor: Numeric structure with character labels sitting on top. For variable with only a few collection of categories.

```{r, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width=6,
  fig.asp=.6,
  out.width= "90%"
)

theme_set(theme_bw()+ theme(legend.position="bottom"))

library(rvest)

library(p8105.datasets)
```

str_detect detects "jeff" to see which one in the string matches "jeff", str_place will replace if find "jeff". We know eaxactly what we want to replace. 

```{r}
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, "jeff")

str_replace(string_vec, "jeff", "Jeff")
```


str_detect(string_vec, "i think") detects every sentence with "i think"
str_detect(string_vec, "^i think") detects only those begin with "i think"
str_detect(string_vec, "i think$") detects those end with "i think"
```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )

str_detect(string_vec, "i think")
str_detect(string_vec, "^i think")

str_detect(string_vec, "i think$")
```

str_detect(string_vec,"[Bb]ush") finds those begin with either upper case or lower case B and ush. 
```{r}
string_vec = c(
  "Y'all remember Pres. HW Bush?",
  "I saw a green bush",
  "BBQ and Bushwalking at Molonglo Gorge",
  "BUSH!!"
  )

str_detect(string_vec,"[Bb]ush")
```

str_detect(string_vec, "^[0-9][a-zA-Z]") finds a number and then follows by any letter 
```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "^[0-9][a-zA-Z]")
```

str_detect(string_vec, "7.11") selects 7 follows by everything and follows by 11
```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
```

Some characters are “special”. These include [ and ], ( and ), and .. If you want to search for these, you have to indicate they’re special using \. Unfortunately, \ is also special. So you need to use two \\.
```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]'
  )

str_detect(string_vec, "\\[")
```

### PULSE data 

This is the way that we recommend you to tidy the PULSE dataset 

```{r}
pulse_data = haven::read_sas("./data/public_pulse_data.sas7bdat") %>%
  janitor::clean_names() %>%
  gather(key = visit, value = bdi, bdi_score_bl:bdi_score_12m) %>%
  mutate(visit = str_replace(visit, "bdi_score_", ""),
         visit = str_replace(visit, "bl", "00m"),
         visit = fct_relevel(visit, str_c(c("00", "01", "06", "12"), "m"))) %>%
  arrange(id, visit)

print(pulse_data, n = 12)
```



