---
title: "data_wrangling_ii_strings_and_factors"
author: "Boya Guo"
date: "10/16/2018"
output: html_document
---

String: just the text, character varaible, no underlying structures 

Factor: Numeric structure with character labels sitting on top. For variable with only a few collection of categories.

```{r, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width=6,
  fig.asp=.6,
  out.width= "90%"
)

theme_set(theme_bw()+ theme(legend.position="bottom"))

library(rvest)

library(p8105.datasets)
```

str_detect detects "jeff" to see which one in the string matches "jeff", str_place will replace if find "jeff". We know eaxactly what we want to replace. 

```{r}
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, "jeff")

str_replace(string_vec, "jeff", "Jeff")
```


str_detect(string_vec, "i think") detects every sentence with "i think"
str_detect(string_vec, "^i think") detects only those begin with "i think"
str_detect(string_vec, "i think$") detects those end with "i think"
```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )

str_detect(string_vec, "i think")
str_detect(string_vec, "^i think")

str_detect(string_vec, "i think$")
```

str_detect(string_vec,"[Bb]ush") finds those begin with either upper case or lower case B and ush. 
```{r}
string_vec = c(
  "Y'all remember Pres. HW Bush?",
  "I saw a green bush",
  "BBQ and Bushwalking at Molonglo Gorge",
  "BUSH!!"
  )

str_detect(string_vec,"[Bb]ush")
```

str_detect(string_vec, "^[0-9][a-zA-Z]") finds a number and then follows by any letter 
```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "^[0-9][a-zA-Z]")
```

str_detect(string_vec, "7.11") selects 7 follows by everything and follows by 11
```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
```

Some characters are “special”. These include [ and ], ( and ), and .. If you want to search for these, you have to indicate they’re special using \. Unfortunately, \ is also special. So you need to use two \\.
```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]'
  )

str_detect(string_vec, "\\[")
```

### PULSE data 

This is the way that we recommend you to tidy the PULSE dataset 

```{r}
pulse_data = haven::read_sas("./data/public_pulse_data.sas7bdat") %>%
  janitor::clean_names() %>%
  gather(key = visit, value = bdi, bdi_score_bl:bdi_score_12m) %>%
  mutate(visit = str_replace(visit, "bdi_score_", ""),
         visit = str_replace(visit, "bl", "00m"),
         visit = fct_relevel(visit, str_c(c("00", "01", "06", "12"), "m"))) %>%
  arrange(id, visit)

print(pulse_data, n = 12)
```

### NSDUH data 

Read in the data from website
```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"
drug_use_xml = read_html(url)

table_marj = (drug_use_xml %>% html_nodes(css = "table")) %>% 
  .[[1]] %>%
  html_table() %>%
  slice(-1) %>%
  as_tibble()
```

Clean up the imported data 

Removes any string contains p-value using "-contains"
```{r}
data_marj = 
  table_marj %>%
  select(-contains("P Value")) %>%
  gather(key = key, value = percent, -State) %>%
  separate(key, into = c("age", "year"), sep = "\\(") %>%
  mutate(year = str_replace(year, "\\)", ""),
         percent = str_replace(percent, "[a-c]$", ""),
         percent = as.numeric(percent)) %>%
  filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
```

Now we have tidy data, we could start making some plots

```{r}
data_marj %>%
  filter(age == "12-17") %>% 
  mutate(State = fct_reorder(State, percent)) %>% 
  ggplot(aes(x = State, y = percent, color = year)) + 
    geom_point() + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Factors

2 2 1 1, list in alphabetical order
```{r}
vec_sex = factor(c("male", "male", "female", "female"))
as.numeric(vec_sex)
vec_sex
```

Changing the reference to "male", and then change to numeric-->becomes 1 1 2 2 
```{r}
vec_sex = relevel(vec_sex, ref = "male")
vec_sex
as.numeric(vec_sex)
```

### Weather data 
```{r, cache =TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```

By default
```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
```

fct_relevel: takes your factor variable and list them to the order you want them to appear
```{r}
weather_df %>%
  mutate(name = forcats::fct_relevel(name, c("Waikiki_HA", "CentralPark_NY", "Waterhole_WA"))) %>% 
  ggplot(aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
```

A second example reordered name according to tmax values in each name using fct_reorder:
```{r}
weather_df %>%
  mutate(name = forcats::fct_reorder(name, tmax)) %>% 
  ggplot(aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
```

Ordering is important in linear regression 
```{r}
weather_df %>%
  lm(tmax ~ name, data = .)

weather_df %>%
  mutate(name = forcats::fct_relevel(name, c("Waikiki_HA", "CentralPark_NY", "Waterhole_WA"))) %>% 
  lm(tmax ~ name, data = .)
```

###NYC Restaurant Inspections

```{r}
data(rest_inspec)

rest_inspec %>% 
  group_by(boro, grade) %>% 
  summarize(n = n()) %>% 
  spread(key = grade, value = n)

rest_inspec =
  rest_inspec %>%
  filter(grade %in% c("A", "B", "C"), boro != "Missing") %>% 
  mutate(boro = str_to_title(boro))
```

Pizza Places
```{r}
rest_inspec %>% 
  filter(str_detect(dba, "Pizza")) %>% 
  group_by(boro, grade) %>% 
  summarize(n = n()) %>% 
  spread(key = grade, value = n)
```

That doesn’t look right – for sure there are more pizza place ratings than that! The problem is that the match in str_detect is case-sensitive until we tell it not to be:
```{r}
rest_inspec %>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>% 
  group_by(boro, grade) %>% 
  summarize(n = n()) %>% 
  spread(key = grade, value = n)
```

The table is okay but I’d like to visualize this.
```{r}
rest_inspec %>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>%
  ggplot(aes(x = boro, fill = grade)) + 
  geom_bar() + 
  scale_fill_viridis(discrete = TRUE)
```

Reorder...Might help to have things in a different order – maybe number of pizza places? Fortunately this can be done using fct_infreq.
```{r}
rest_inspec %>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>%
  mutate(boro = fct_infreq(boro)) %>%
  ggplot(aes(x = boro, fill = grade)) + 
  geom_bar() + 
  scale_fill_viridis(discrete = TRUE)
```

Change a factor value. Suppose I want to rename a boro; I’ll try to do this using replace.
```{r}
rest_inspec %>% 
  filter(str_detect(dba, "[Pp][Ii][Zz][Zz][Aa]")) %>%
  mutate(boro = fct_infreq(boro),
         boro = replace(boro, which(boro == "Brooklyn"), "HipsterHQ")) %>%
  ggplot(aes(x = boro, fill = grade)) + 
  geom_bar() + 
  scale_fill_viridis(discrete = TRUE)

```
That didn’t work at all! Factors have very specific values, trying to use a value that is not an existing factor level won’t work. Fortunately there is a dedicated function for renaming factor levels:
```{r}
rest_inspec %>% 
  filter(str_detect(dba, regex("pizza", ignore_case = TRUE))) %>%
  mutate(boro = fct_infreq(boro),
         boro = fct_recode(boro, "HipsterHQ" = "Brooklyn")) %>%
  ggplot(aes(x = boro, fill = grade)) + 
  geom_bar() + 
  scale_fill_viridis(discrete = TRUE)
```