---
title: "Data Manipulation"
author: "Boya Guo"
date: "9/20/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

`````

## Import FAS csv files 

Import my first csv to use as an example.

```{r}
litters_data = read_csv("./data/FAS_litters.csv",
  col_types = "ccddiiii")
litters_data = janitor::clean_names(litters_data)

pups_data = read_csv("./data/FAS_pups.csv",
  col_types = "ciiiii")
pups_data = janitor::clean_names(pups_data)
`````

## Select variabels 

...by listing 

```{r}
select (litters_data, group, litter_number, gd0_weight)
select (litters_data, litter_number, gd0_weight, pups_survive)
`````

... by specifying a range
```{r}
select (litters_data, gd_of_birth: pups_survive)
select (litters_data, group, gd_of_birth: pups_survive)
`````

...by saying what you want to remove 
```{r}
select (litters_data, -litter_number)
`````

...selecting and renaming
```{r}
select (litters_data, group, litter_number, gest_day_0_weight= gd0_weight)
`````
```{r}
rename (litters_data, gest_day_0_weight= gd0_weight)
`````

...use select helpers
```{r}
select (litters_data, starts_with("gd"))
select (litters_data, litter_number, starts_with("gd"))

select(litters_data, litter_number, everything())
`````

...Learning assignment 
```{r}
select(pups_data, litter_number, sex, pd_ears)
````

## Filter observations 

do some filitering 

```{r}
filter(litters_data, gd0_weight<225)
filter(litters_data, gd0_weight >=225)
filter(litters_data, pups_born_alive==225)
````

is it true that gd0_weight is missing 

```{r}
filter(litters_data, is.na(gd0_weight))
````

exclude gd0_weight=missing 
```{r}
filter(litters_data, !is.na(gd0_weight))
````

filter group=Low 8 or group=Low7.Two ways below:
```{r}
filter(litters_data, group=="Low8"| group=="Low7")
````
```{r}
filter(litters_data, group %in% c("Low8", "Low7"))
````

filter pups_born_alive is 4 to 6: 
```{r}
filter(litters_data, pups_born_alive %in% 4:6)
````

filter first condition giving the second condition is also true:
```{r}
filter(litters_data, pups_born_alive %in% 4:7,!is.na(gd0_weight))
````

## Mutate 

create variables (added to the end of dataset), and changed to lower case

```{r}
mutate(litters_data, 
wt_gain=gd18_weight -gd0_weight,
group=tolower(group))

mutate(litters_data, 
wt_gain=gd18_weight -gd0_weight,
wt_gain=wt_gain^2)
````


## Arrange 

Arrange the data by gd0_weight from the smallest weight to the largest weight. 

Can also arrange by serveral things: frist by pups_born_alive then by gd0_weight:  

```{r}
arrange(litters_data, gd0_weight)
arrange(litters_data, pups_born_alive, gd0_weight)
arrange(litters_data, desc(pups_born_alive), gd0_weight)

````


