---
title: "EDA"
author: "Boya Guo"
date: "10/4/2018"
output: github_document
---

```{r}
library(tidyverse)
```

```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

Data import.

We created a new variable called montg, created using lubridate::floor_date().Lubridate is the package that designs for you to manipulation in date variables.Round down the date to the nearest month.   

```{r data_import, cache=TRUE}
library(rnoaa)

weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10,
  month = lubridate::floor_date(date, unit = "month")) %>%
  select(name, id, everything())

weather_df

View(weather_df)
```

##  Start grouping 

group by (): insert the varaible that you are interested in grouping by. 

In the Console pane, you will see: For example: Groups: nam, month [36]. The 36 in the bracket is the distinct number of pairs with the grouping order. 

Use the ungroup, you could ungroup any groups you have.

```{r}
weather_df %>% 
  group_by(name)
```
```{r}
weather_df %>% 
  group_by(name,month)
```

Summarize:  summarize (number=n())： how many elements in each group. Create a summary inside of the group.

```{r}
weather_df %>% 
   group_by(name,month) %>%
  summarize(number = n())
```

```{r}
weather_df %>% 
   group_by(name) %>%
  summarize(number=n())
```

```{r}
weather_df %>% 
   group_by(month) %>%
  summarize(number=n())
```

Other summary functions...
  
```{r}
weather_df %>% 
   count(month) 
```
```{r}
weather_df %>% 
   count(name, month) 
```

## Group summaries 

```{r}
weather_df %>% 
   group_by(name, month) %>%
  summarize(number=n(),
            mean_tmax =mean(tmax))%>% View 
```
Look at the table output, you will find that Waikiki_HA have some missing values. R will convert mean whnen there is a missing vaule in the group.

We could address this...

num_na = sum(is.na(tmax)): is tmax missing yes/no, if it is NA it will give me a true, otherwise it will give me a false. Create a variable called num_na, which summarizes the total number of the missing observations.
 
```{r}
weather_df %>% 
   group_by(name, month) %>%
  summarize(number=n(),
            num_na = sum(is.na(tmax)),
            mean_tmax =mean(tmax))%>% View 
```

If we want to omit the missing values...
?mean. We found out that na.rm function strips NA vaules. 

```{r}
weather_df %>% 
   group_by(name, month) %>%
  summarize(number=n(),
            mean_tmax =mean(tmax, na.rm=TRUE),
            median_prcp =median(prcp, na.rm=TRUE),
            sd_tmin = sd(tmin, na.rm=TRUE))
```

If use mutate, it will fill out the mean tmax for each name, but will not have differnt mean tmax for each group.
```{r}
weather_df %>% 
   group_by(name) %>%
  mutate(mean_tmax=mean(tmax, na.rm=TRUE))
```

This is still a tibble! 

```{r}
month_df = weather_df %>% 
  group_by(name, month) %>% 
  summarize(number = n(),
            mean_tmax = mean(tmax, na.rm = TRUE),
            median_prcp = median(prcp, na.rm = TRUE),
            sd_tmin = sd(tmin, na.rm = TRUE)) 
```

plot two tibbles at once...
```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(alpha = .5) + 
  geom_line(data = month_df, aes(x = month, y = mean_tmax))
```

Tidy is not always the best...
Use the speard function to make data more readable.

```{r}
weather_df %>% 
  group_by(name, month) %>% 
  summarize(mean_tmax = mean(tmax, na.rm = TRUE)) %>% 
  spread(key = name, value = mean_tmax) %>% 
  knitr::kable(digits = 3)
```

## Grouped mutate 

You will get a month by month mean_tmax value 
```{r}
weather_df %>% 
  group_by(name, month) %>% 
  mutate(mean_tmax = mean(tmax, na.rm = TRUE))
```

A more interesting example ...

The mean_tmax: takes the average temprature of Central Park and repeated everywhere in the dataset. 
The second line uses the tmax value minus the mean for each group. 

We can then make a plot to see what does it look like. 
 
```{r}
weather_df %>%
  group_by(name) %>%
  mutate(mean_tmax=mean(tmax, na.rm= TRUE),
         centered_tmax=tmax-mean_tmax) %>% 
ggplot(aes(x = date, y = centered_tmax, color = name)) +
  geom_point()
```

## Windows function 

The previous example used mean() to compute the mean within each group, which was then subtracted from the observed max tempurature. mean() takes n inputs and produces a single output.

Window functions, in contrast, take n inputs and return n outputs, and the outputs depend on all the inputs. 

Use ranks... 

```{r}
weather_df %>% 
  group_by(name, month) %>% 
  mutate(tmax_rank = min_rank(desc(tmax))) %>% 
  filter(tmax_rank < 2)
```

lag function...

Offsets, especially lags, are used to compare an observation to it’s previous value. This is useful, for example, to find the day-by-day change in max temperature within each station over the year:

```{r}
weather_df %>% 
  group_by(name) %>% 
  mutate(lag_tmax = lag(tmax))
```

## How neat is this?

How much does the temperature change from onr day to anothetr day? Then can calculate the standard deviation of one day change of each location. 

```{r}
weather_df %>% 
  group_by(name) %>% 
  mutate(one_day_change = tmax - lag(tmax)) %>% 
  summarize(sd_one_day_change = sd(one_day_change, na.rm = TRUE))
```


