---
title: "Iteration and List Columns"
author: "Boya Guo"
date: "2018年10月30日"
output: github_document
---

```{r}
library(tidyverse)

set.seed(1)
```

### List 

In R, vectors are limited to a single data class – all elements are characters, or all numeric, or all logical. Trying to join the following vectors will result in coersion, as would creating vectors of mixed types.

```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

Lists contain indexed elements, and the indexed elements themselves be scalars, vectors, or other things entirely.
```{r}
l = list(vec_numeric = 5:8,
         mat         = matrix(1:8, 2, 4),
         vec_logical = c(TRUE, FALSE),
         summary     = summary(rnorm(1000)))
l
```

```{r}
l$vec_numeric

l[[1]]

l[[1]][1:3]
```


### for loops

```{r}
df = data_frame(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)

is.list(df)
```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}

mean_and_sd(df[[1]])

mean_and_sd(df[[2]])

mean_and_sd(df[[3]])

mean_and_sd(df[[4]])
```

for loop
```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(df[[i]])
}
```

### let's try a different function using "map"" 

```{r}
output = map(df, mean_and_sd)
```

### map variants 

```{r}
output = map_dbl(df, median, .id = "input")

output = map_dfr(df, mean_and_sd, .id = "input")
```


```{r}
output = map2(.x = input_1, .y = input_2, ~func(arg_1 = .x, arg_2 = .y))
```

### Napoleon example 

```{r}
library(rvest)

read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  data_frame(title, stars, text)
}
```

Use this function to read the five pages of reviews on the URLs defined in the code chunk below.

```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

output = vector("list", 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews = bind_rows(output)

dynamite_reviews = map_df(vec_urls, read_page_reviews)
```


Review weather dataset

```{r}
library(rnoaa)

weather = 
  meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2016-01-01",
                      date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
weather_nest = 
  nest(weather, date:tmin)

weather_nest
```

```{r}
weather_nest %>% pull(name)

weather_nest %>% pull(id)

weather_nest %>% pull(data)
```

### Operations on list columns

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nest$data[[1]])

map(weather_nest$data, weather_lm)
```

```{r}
weather_nest = 
  weather_nest %>% 
  mutate(models = map(data, weather_lm))

weather_nest
```


