---
title: "Visualization Pt1"
author: "Boya Guo"
date: "9/27/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
```

```{r data_import, cache=TRUE}
library(rnoaa)

weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df

View(weather_df)
```

## Start a plot 

Blank plot 
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))
```

Scatterplot (add gemo points to the plot)
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

A scatterplot focues only on Central Park: 
```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Name the ggplot: 

```{r}
weather_sp = 
  ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

## More plot options 

Add an aesthetic: 

color based on different names:

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```

Add a geomtry: 

gemo_smooth: add a smooth line in the graph. Se=FALSE: trun off the confidence interval on the plot.  
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))+
  geom_smooth (Se=FALSE)
```

Adjust the transparency level of points. In this case maping exists only inside of the geom_point. 
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha=0.4)+
  geom_smooth (Se=FALSE)
```

What if we put color=name inside of the aes(). Right now, the aestheic mapping is defined anywhere of all the geom_point on the map. 
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.4) + 
  geom_smooth(se = FALSE)
```

Facetting...

create seperate panes for the name variables: 
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha=0.4)+
  geom_smooth (Se=FALSE)+ 
  facet_grid( ~ name)
```

A more interesting plot...

see the max temp of the year, and add the size of these point.

geom_line: instead of dots, show lines connect the points 

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name, size = prcp)) +
  geom_point() + 
  geom_smooth(se = FALSE) + 
  facet_grid(~name)
```


