---
title: "Writing functions"
author: "Boya Guo"
date: "10/25/205"
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(rvest)
set.seed(1)
theme_set(theme_bw() + theme(legend.position = "bottom"))
```


### Normal distribution function 
```{r}
x = rnorm(25, mean = 5, sd = 3)

(x - mean(x)) / sd(x)
```

### Z score function 
```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  z
  
}

z_scores(x)
```

Check to see if this works...
```{r}
y=runif(100)
z_scores(y)
```

Compute z score for 3, character factor, and Ture/False. My function works for wha I anticipated.
```{r error=TRUE}
z_scores(3)

z_scores("my name is jeff")

z_scores(iris)

z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

### Condtional evaluation. 

First check if the input numeric or not. If false, will do nothing and move to the next step to check if length is 1 or not. 
```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}
```

```{r error=TRUE}
z_scores(3)

z_scores("my name is jeff")

z_scores(iris)

z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

### Multiple output 
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  list(mean = mean_x, 
       sd = sd_x)
}
```

### Store values in a data frame 

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

### Multiple inputs 
```{r}

```

