---
title: "Writing functions"
author: "Boya Guo"
date: "10/25/205"
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(rvest)
set.seed(1)
theme_set(theme_bw() + theme(legend.position = "bottom"))
```


### Normal distribution function 
```{r}
x = rnorm(25, mean = 5, sd = 3)

(x - mean(x)) / sd(x)
```

### Z score function 
```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  z
  
}

z_scores(x)
```

Check to see if this works...
```{r}
y=runif(100)
z_scores(y)
```

Compute z score for 3, character factor, and Ture/False. My function works for wha I anticipated.
```{r error=TRUE}
z_scores(3)

z_scores("my name is jeff")

z_scores(iris)

z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

### Condtional evaluation. 

First check if the input numeric or not. If false, will do nothing and move to the next step to check if length is 1 or not. 
```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}
```

```{r error=TRUE}
z_scores(3)

z_scores("my name is jeff")

z_scores(iris)

z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

### Multiple output 
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  list(mean = mean_x, 
       sd = sd_x)
}
```

### Store values in a data frame 

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

### Multiple inputs 

Look at simple linear regression...

```{r}
sim_data = tibble(
  x = rnorm(30, mean = 1, sd = 1),
  y = 2 + 3 * x + rnorm(30, 0, 1)
)

ls_fit = lm(y ~ x, data = sim_data)
  
beta0_hat = coef(ls_fit)[1]
beta1_hat = coef(ls_fit)[2]
```

```{r}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 1, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, 1)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}
```

```{r}
sim_regression(n = 3000, beta0 = 0, beta1 = -1)

sim_regression(n = 3000)

sim_regression(300, 2, 3)
```

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-title") %>%
  html_text()

review_stars = dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = dynamite_html %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

Write a function to extract reviews...
```{r}
read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  review_titles = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  review_stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  review_text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}


url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(urls[1]),
  read_page_reviews(urls[2]),
  read_page_reviews(urls[3]),
  read_page_reviews(urls[4]),
  read_page_reviews(urls[5])
)

dynamite_reviews
```

